Case Study: scRNA-seq (Mouse data, scDD method)

### 2018-03-27 datasets/GWAS/GWAS.Rmd
Change covariateHeatmap function name to covariateLinePlot

```{r, fig.width=8, fig.height=3.5}
mcols(sbN)$ind_covariate <- mcols(sbN)$ind_covar_N
mcols(sbN)$tstat <- bmi %>% filter(!is.na(ind_covar_N)) %>% pull(effect_size)
covariateHeatmap(sbN, alpha=0.05, covname="tstat", nbins=25, 
                 linePlot = TRUE, trans="log1p")
covariateHeatmap(sbN, alpha=0.05, covname="ind_covar_N", nbins=25, 
                 linePlot = TRUE, trans="log1p")
```

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sbAF)$ind_covariate <- abs(mcols(sbAF)$ind_covar_AF-0.5)
mcols(sbAF)$tstat <- bmi %>% filter(!is.na(ind_covar_AF)) %>% pull(effect_size)
covariateHeatmap(sbAF, alpha=0.05, covname="tstat", nbins=25, 
                 linePlot = TRUE, trans = "log1p")
covariateHeatmap(sbAF, alpha=0.05, covname="ind_covar_AF", nbins=25, 
                 linePlot = TRUE)
```

>>>>

```{r, fig.width=8, fig.height=3.5}
mcols(sbN)$ind_covariate <- mcols(sbN)$ind_covar_N
mcols(sbN)$tstat <- bmi %>% filter(!is.na(ind_covar_N)) %>% pull(effect_size)
covariateLinePlot(sbN, alpha=0.05, covname="tstat", nbins=25, 
                 linePlot = TRUE, trans="log1p")
covariateLinePlot(sbN, alpha=0.05, covname="ind_covar_N", nbins=25, 
                 linePlot = TRUE, trans="log1p")
```

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sbAF)$ind_covariate <- abs(mcols(sbAF)$ind_covar_AF-0.5)
mcols(sbAF)$tstat <- bmi %>% filter(!is.na(ind_covar_AF)) %>% pull(effect_size)
covariateLinePlot(sbAF, alpha=0.05, covname="tstat", nbins=25, 
                 linePlot = TRUE, trans = "log1p")
covariateLinePlot(sbAF, alpha=0.05, covname="ind_covar_AF", nbins=25, 
                 linePlot = TRUE)
```

### 2018-03-27 datasets/scrnaseq/scrnaseq-human-mast.Rmd
Change covariateHeatmap function name to covariateLinePlot

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")
```

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("MAST, Covariate 2: Detection Rate")
```

>>>>

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateLinePlot(sb1, alpha=0.05, covname="ind_covariate", nbins=25) +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")
```

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
covariateLinePlot(sb2, alpha=0.05, covname="ind_covariate", nbins=25) +
  ggtitle("MAST, Covariate 2: Detection Rate")
```

### 2018-03-27 datasets/scrnaseq/scrnaseq-human-scdd.Rmd
Change covariateHeatmap function name to covariateLinePlot

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("scDD, Covariate 2: Detection Rate")
```

>>>>

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateLinePlot(sb1, alpha=0.05, covname="ind_covariate", nbins=25) +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

@@

```{r, fig.width=8, fig.height=3.5}
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
covariateLinePlot(sb2, alpha=0.05, covname="ind_covariate", nbins=25) +
  ggtitle("scDD, Covariate 2: Detection Rate")
```

### 2018-03-27 datasets/scrnaseq/scrnaseq-mouse-mast.Rmd
Change covariateHeatmap function name to covariateLinePlot

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE, trans = "log1p") +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")
```

>>>>

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateLinePlot(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 trans = "log1p") +
  ggtitle("MAST, Covariate 1: Mean Nonzero Expression")
```

### 2018-03-27 datasets/scrnaseq/scrnaseq-mouse-scdd.Rmd
Change covariateHeatmap function name to covariateLinePlot

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateHeatmap(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE, trans = "log1p") +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

@@

# properties of method-exclusive discoveries
methods <- c("ashs", "lfdr", "ihw-a10", "bl-df03", "qvalue", "bh", "bonf",
             "scott-empirical", "scott-theoretical")
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
plotCovariateBoxplots(sb2, alpha=0.1, nsets=6, methods=methods, maxNum=3) +
  ggtitle("scDD, Covariate 2: Detection Rate")

```
```{r, fig.width=8, fig.height=3.5}
covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate") +
  ggtitle("scDD, Covariate 2: Detection Rate")

covariateHeatmap(sb2, alpha=0.05, covname="ind_covariate", nbins=25, 
                 linePlot = TRUE) +
  ggtitle("scDD, Covariate 2: Detection Rate")
```

>>>>

```{r, fig.width=8, fig.height=3.5}
mcols(sb1)$ind_covariate <- mcols(sb1)$meanExp
covariateLinePlot(sb1, alpha=0.05, covname="ind_covariate", nbins=25, 
                 trans = "log1p") +
  ggtitle("scDD, Covariate 1: Mean Nonzero Expression")
```

@@

```
```{r, fig.width=8, fig.height=3.5}
mcols(sb2)$ind_covariate <- mcols(sb2)$detection
covariateLinePlot(sb2, alpha=0.05, covname="ind_covariate", nbins=25) +
  ggtitle("scDD, Covariate 2: Detection Rate")
```
